Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-04-10 Paper/paper.tex
Update text

\begin{figure*}
  \begin{center}
    % rtg2.draw_g_paper() 
    \includegraphics[scale=0.65]{g.pdf}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionisation rate,
    assuming 100\% escape fraction.  Model luminosity functions are
    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
    the right panel.  The solid black curve shows the hydrogen
    photoionisate rate in our best-fit global model, and the yellow
    curves show a random sample from the global posterior.  The red
    points with error bars in this figure show the measurements of
    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
    forest, and the orange points show the measurements by
    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
    dashed green curve shows the hydrogen photoionisation rate
    evolution in the model of \citet{2012ApJ...746..125H}, while the
    solid green curve shows the contribution of quasars to it. }
  \label{fig:gammapi}
\end{figure*}

@@

The 1~Ry emissivity can now be used to calculate the ionizing flux and
photoionization rate contributed by quasars.  The frequency dependence
above 1~Ry is given by Equation~(\ref{eqn:sed}) or
(\ref{eqn:sed_faint}), so that for $\nu > \nu_{912}$
\begin{equation}
  \epsilon_\nu = \epsilon_{912}\left(\frac{\nu}{\nu_{912}}\right)^\alpha,
  \label{eqn:epsilon_freq}
\end{equation}
where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$
(Equation~\ref{eqn:sed_faint}).  The flux in the IGM is
written as a solution of the cosmological radiative transfer equation
as \citep{2012ApJ...746..125H}
\begin{multline}
  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}\frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
  \times\exp{(-\tau_\mathrm{eff}(\nu_0, z_0, z))},
  \label{eqn:flux}
\end{multline}
where
\begin{equation}
  \nu = \nu_0\left(\frac{1+z}{1+z_0}\right).
\end{equation}
Here the effective optical depth is estimated as
\begin{equation}
  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
\end{equation}
where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$ and the column density
distribution $f(N_\mathrm{HI}, z)$ is taken to be a power law \citep{2013MNRAS.436.1023B}
\begin{equation}
  f(N_\mathrm{HI}, z) = \frac{A}{N_\mathrm{LL}}\left(\frac{N_\mathrm{HI}}{N_\mathrm{LL}}\right)^{-\beta_N}\left(\frac{1+z}{4.5}\right)^{-\beta_z},
\end{equation}
with $A=0.93$, $\beta_N=1.33$, $\beta_z=1.92$, and
$N_\mathrm{LL}=10^{17.2}$~cm$^{-2}$.  The hydrogen photoionization
rate is then given by
\begin{equation}
  \Gamma_\mathrm{HI}=4\pi\int_{\nu_{912}}^\infty d\nu \frac{j(\nu,z)}{h\nu} \sigma(\nu),
\end{equation}
where $\sigma$ is the photoionization cross-section.  The result is
shown in Figure~\ref{fig:gammapi}, in which as before the solid black
curve shows the hydrogen photoionisate rate in our best-fit global
model, and the yellow curves show a random sample from the global
posterior.  Also, as before, the right panel of
Figure~\ref{fig:gammapi} shows the result when we only account for
quasars brighter than $M_{1450}=-20$, while the left panel shows the
result when the integration limit is $M_{1450}=-18$.  The red points
with error bars in this figure show the measurements of
\citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$ forest,
and the orange points show the measurements by
\citet{2011MNRAS.412.2543C} from quasar proximity zones.  The dashed
green curve shows the hydrogen photoionisation rate evolution in the
model of \citet{2012ApJ...746..125H}, while the solid green curve
shows the contribution of quasars to it.

The black open circles show the photoionisation rate values derived
from our fits in the individual redshift bins.  However, note that
unlike in the global model it is not possible to do the integral in
Equation~(\ref{eqn:flux}) for these individual fits.  We can only
derive the photoionisatoin rate by assuming what is known as the local
source approximation, that is by assuming that the photons emitted at
redshift $z$ are absorbed at the same redshift without propagation to
large distances.

In the local source approximation, Equation~(\ref{eqn:flux}) becomes
\begin{equation}
  j(\nu_0, z_0) = \frac{1}{4\pi}\lambda_\mathrm{mfp}(\nu_0, z_0)\epsilon(\nu_0, z_0),
\end{equation}
where $\lambda_\mathrm{mfp}$ is the mean free path.  The hydrogen
photoionization rate is given by
\begin{equation}
  \Gamma_\mathrm{HI}=4\pi\int_{\nu_{912}}^\infty d\nu \frac{j_\nu}{h\nu} \sigma(\nu),
  \label{eqn:gammapi}
\end{equation}
where $\sigma$ is the ionization cross-section
\begin{equation}
  \sigma(\nu) = \sigma_0\left(\frac{\nu}{\nu_{912}}\right)^{-3},
  \label{eqn:sigma}
\end{equation}
with $\sigma_0=6.3\times 10^{-18}$~cm$^2$ \citep{2006agna.book.....O}.
In the redshift range $z=2.3$--$5.5$, the mean free path is measured
to be \citep{2014MNRAS.445.1745W}
\begin{equation}
  \lambda_\mathrm{mfp}(\nu, z)= \lambda_0\left(\frac{1+z}{5}\right)^{-5.4}\left(\frac{\nu}{\nu_{912}}\right)^{1.5},
  \label{eqn:mfp}
\end{equation}
where the frequency dependence comes from the assumed column density
distribution $f(N_\mathrm{HI})\propto N_\mathrm{HI}^{-1.5}$.  We
extrapolate the redshift dependence in Equation~(\ref{eqn:mfp}) at
$z<2.3$ and $z>5.5$.  Combining Equations~(\ref{eqn:epsilon_freq}),
(\ref{eqn:sigma}), and (\ref{eqn:mfp}), Equation~(\ref{eqn:gammapi})
gives
\begin{multline}
  \Gamma_\mathrm{HI}=4.6\times 10^{-13} \mathrm{s}^{-1} \left(\frac{\epsilon_{912}}{10^{24}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}}\right)\\
  \times\left(\frac{1}{1.5-\alpha}\right)\left(\frac{1+z}{5}\right)^{-2.4}.
\end{multline}
Note that this equation refers to the \emph{comoving} emissivity.  The
local source approximation works well for $z>3$, as can be seen in
Figure~\ref{fig:gammapi}, where the points from the individual fits
are in much better agreement with the curves from the global model.
At lower redshift, the photoionisation rate in the individual models
is much higher than that in the global model, because the individual
models overestimate the flux at these redshifts.

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth,keepaspectratio]{evolution.pdf}
%%   \end{center}
%%   \caption{Parameter evolution from individual fits.  Coloured points
%%     show results when Giallongo quasars are not included.  Black
%%     points show results when Giallongo quasars are included.}
%% \end{figure*}

%% \begin{figure}
%%   \begin{center}
%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal_dense.pdf}
%%   \end{center}
%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
%% \end{figure}

%% \begin{figure}
%%   \begin{center}
%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff.pdf}
%%   \end{center}
%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
%% \end{figure}

%% \begin{figure}
%%   \begin{center}
%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff_ind.pdf}
%%   \end{center}
%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
%% \end{figure}

@@

%% The discrepancy is about a
%% factor of two instead of five.

>>>>

\begin{figure*}
  \begin{center}
    % rtg2.draw_g_paper() 
    \includegraphics[scale=0.65]{g.pdf}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionisation rate,
    assuming unit escape fraction, when the AGN luminosity function is
    integrated down to $M_{1450}=-21$ (blue curve and shaded region)
    and $M_{1450}=-18$ (red curve and shaded region).  The shaded
    regions show the one-sigma (68.26\%) uncertainty.  Also shown are
    the photoionization rate measurements by \citet[filled
      circles]{2013MNRAS.436.1023B}, \citet[inverted
      triangles]{2011MNRAS.412.2543C}, and
    \citet[pentagons]{2017MNRAS.467.3172G}, and models of
    \citet[dotted brown curve]{2012ApJ...746..125H}, the QSO
    contribution in this model (dashed grey), \citet[dashed
      brown]{2015ApJ...813L...8M}, the QSO contribution from the model
    of \citet[dashed orange]{2015MNRAS.451L..30K}, \citet[dotted
      grey]{2017ApJ...837..106O}, and \citet[dashed
      grey]{2018arXiv180104931P}.}
  \label{fig:gammapi}
\end{figure*}

@@

The 912\,\AA\ emissivity can now be used to calculate the hydrogen
ionizing flux and the hydrogen photoionization rate contributed by
AGN.  This adds an additional layer of uncertainty as the \HI\ column
density structure of the IGM has not been measured at all redshifts of
interests, thereby requiring uncertain extrapolation.  The frequency
dependence of the AGN SED above 1~Ry is given by
Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint}), so that for $\nu >
\nu_{912}$
\begin{equation}
  \epsilon_\nu = \epsilon_{912}\left(\frac{\nu}{\nu_{912}}\right)^\alpha,
  \label{eqn:epsilon_freq}
\end{equation}
where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$
(Equation~\ref{eqn:sed_faint}).  We assume that faint AGN
($M_{1450}>-23$) have the shallower spectral slope.  The flux in the
IGM is written as a solution of the cosmological radiative transfer
equation as \citep{2012ApJ...746..125H}
\begin{multline}
  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}
  \frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
  \times\exp{(-\tau_\mathrm{eff}(\nu_0, z_0, z))},
  \label{eqn:flux}
\end{multline}
where
\begin{equation}
  \nu = \nu_0\left(\frac{1+z}{1+z_0}\right).
\end{equation}
Here the effective optical depth is estimated as
\begin{equation}
  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty
  dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
\end{equation}
where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$.  (We ignore the small
contribution of helium to the opacity.)  We assume the \HI\ column
density distribution given by \citet{2012ApJ...746..125H}.  The
\HI\ photoionization rate is then given by
\begin{equation}
  \Gamma_\mathrm{HI}=\int_{\nu_{912}}^\infty d\nu
  \frac{4\pi j(\nu,z)}{h\nu} \sigma(\nu),
\end{equation}
where $\sigma$ is the photoionization cross-section.  We assume an
upper limit of $z=15$ while integrating Equation~(\ref{eqn:flux}).
The result is shown in Figure~\ref{fig:gammapi} for the luminosity
function integration limits of $M_{1450}=-21$ and $-18$.  Also shown
for comparison are the measurements of \citet{2013MNRAS.436.1023B},
derived from the Lyman-$\alpha$ forest, and the measurements by
\citet{2011MNRAS.412.2543C} from quasar proximity zones.  For an
integration limit of $M_{1450}=-21$ the AGN contribution to the
hydrogen photoionization rate falls short of 100\% across the redshift
range.  It is marginally consistent with the measured photoionization
rate at $z=2.4$.  The photoionization rate in our model for
$M_{1450}=-21$ has the same evolution but a higher amplitude by a
factor of $\sim 2$ as the QSO contribution to the \HI\ photoionization
rate in the model of \citet{2012ApJ...746..125H}.  For both of our
integration limits, the photoionisation rate peaks at $z\sim 2$.  For
the integration limit of $M_{1450}=-18$, AGN can provide all the flux
necessary to explain the observed \lya forest between $z=2.4$ and
$3.2$, with a contribution from other sources necessary only at higher
redshifts.  The photoionization rate in the $M_{1450}<-18$ case also
agrees with the inference of \citet{2017MNRAS.467.3172G} from the
low-redshift ($z<0.6$) \lya\ data.  We discuss this low-redshift
evolution in greater detail in the next section.

An important conclusion from Figure~\ref{fig:gammapi} is that the AGN
contribution to hydrogen reionization is likely subdominant, although
it can be non-negligible if faint AGN down to $M_{1450}=-18$ emit
hydrogen-ionizing photons with our assumed SED and a unit escape
fraction.  At $z=6.1$, AGN with $M_{1450}<-18$ contribute about $10\%$
of the required \HI\ ionizing flux.  The contribution of
$M_{1450}<-21$ at this redshift is $\sim 3\%$.  At $z=6$, our
determinations are lower than those by \citet{2015AA...578A..83G} by
almost an order of magnitude.  This difference arises from the
difference in the inferred emissivities in our models relative to
\citet{2015AA...578A..83G}, as discussed in the previous section.  The
photoionization rate evolution in the model of
\citet{2015ApJ...813L...8M} agrees with our determination at low
redshifts ($z<0.5$) for $M_{1450}<-18$ but is much higher at $z>4$, as
expected from the higher emissivities assumed by these authors.  At
$3<z<6$ our model photoionization rates are understandably lower than
those in the models of \citet{2017ApJ...837..106O} and
\citet{2018arXiv180104931P} as these authors include contribution to
the photoionization rate from galaxies in their models. The
differences in our model from that of \citet{2015MNRAS.451L..30K} are
a result of our differences from the reported emissivities of
\citet{2009MNRAS.392...19C} and \citet{2013A&A...551A..29P}, which are
used by \citet{2015MNRAS.451L..30K} to derive an emissivity evolution
model.

@@
